Community biomass and species richness temporal trends reveal contrasting assembly and disassembly processes in natural food-webs

### 2022-07-18 paper/appendix.Rmd
Clean Rsq table and figure 3

theme_set(mytheme)
options(knitr.table.format = "latex")
```
```{r}
var_analysis <- c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "log_bm_std",
  "piel_bm", "piel_nind")
```

@@

```{r}
loadd(
  pred_bm_rich_mono_stable_trends,
  model_bm_rich_int_mono_stable_trends,
  model_bm_rich_int_mono_stable_trends,
  rsq_table_bm_rich_mono_stable_trends
)
```

```{r}
reg_table_bm_rich_mono_stable_trends %>%
  mutate(
    response = str_replace_all(response, var_replacement()),
    term = str_replace_all(term, var_replacement())
    ) %>%
kable(., booktabs = TRUE,
  row.names = FALSE,
  caption =
    paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of community biomass and the temporal trends
      of the network structure."),
      label = "reg"
      ) %>%
  kable_styling(latex_options = c("scale_down", "striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
table_rsq_tps <- rsq_table_bm_rich_mono_stable_trends %>%
  mutate(
    Response = str_replace_all(Response, var_replacement())
  )
table_rsq_tps %>%
  kable(., booktabs = TRUE,
    caption =
      paste0(
      "Marginal and conditional squared R for temporal models."),
  label = "rsq"
      ) %>% #
  kable_styling(latex_options = c("striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

```{r}
loadd(
  sp_anova_table_bm_rich_mono_stable_trends,
  sp_rsq_table_bm_rich_mono_stable_trends
)
```

```{r}
sp_anova_table_bm_rich_mono_stable_trends %>%
  mutate(
    response = str_replace_all(response, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(.,
    booktabs = TRUE,
    row.names = FALSE,
    caption =
      paste0(
      "ANOVA results for the links among the spatial variation of community
      biomass and species richness and the one of network structure."),
  label = "aov-sp"
  ) %>%
  kable_styling(latex_options = c("scale_down", "striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
sp_rsq_table_bm_rich_mono_stable_trends %>%
  mutate(
    Response = str_replace_all(Response, var_replacement())
  ) %>%
  kable(., booktabs = TRUE,
    caption =
      paste0("Marginal and conditional $R^2$ for the spatial models."),
  label = "rsq-sp"
      ) %>% #
  kable_styling(latex_options = c("striped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

>>>>

theme_set(mytheme)
options(knitr.table.format = "latex")
```
```{r}
var_analysis <- c("ct_ff", "w_trph_lvl_avg", "log_rich_std", "log_bm_std")
```

@@

```{r}
loadd(sem_tps)
```

```{r}
map_dfr(sem_tps, piecewiseSEM::rsquared) %>%
  mutate(
    Response = str_replace_all(Response, var_replacement())
  ) %>%
  select(Response, R.squared) %>%
  kable(., booktabs = TRUE,
    caption =
      paste0(
      "Marginal R-squared for temporal models."),
  label = "rsq"
      ) %>% #
  kable_styling(latex_options = c("striped"))
```

@@

```{r}
loadd(sp_sem)
```

```{r}
map_dfr(sp_sem, piecewiseSEM::rsquared) %>%
  mutate(
    Response = str_replace_all(Response, var_replacement())
  ) %>%
  select(Response, Marginal, Conditional) %>%
  mutate(
    Response = str_replace_all(Response, var_replacement()),
    Marginal = round(Marginal, 2),
    Conditional = round(Conditional, 2)
  ) %>%
  kable(., booktabs = TRUE,
    caption =
      paste0("Marginal and conditional $R^2$ for the spatial models."),
  label = "rsq-sp"
      ) %>% #
  kable_styling(latex_options = c("striped"))
```

### 2022-07-18 paper/manuscript.Rmd
Clean Rsq table and figure 3

```{r}
sp_semeff_tab <- from_semEff_to_table(sp_semeff)
semeff_tab <- from_semEff_to_table(semeff)
semeff
semeff_tot <- rbind(
  tibble(semeff_tab, model = "temporal"),
  tibble(sp_semeff_tab, model = "spatial")
  ) %>%
filter(
  !predictor %in% c("log_RC1", "log_RC2"),
  effect_type != "mediators"
)
```

@@

```{r std-old, eval = FALSE, fig.cap=std_cap, fig.width=6}
#loadd(fig_std_coef)
std_table_bm_rich_mono_stable_trends %>%
  filter(
    term %in% c("log_rich_std", "log_bm_std"),
    !response %in% "piel_nind") %>%
  mutate_at(vars(term, response), ~str_replace_all(., var_replacement(
        several_lines = TRUE))) %>%
  mutate(
    type = str_to_sentence(type),
    type = factor(type, levels = c("Temporal", "Spatial"))) %>%
  ggplot(aes(y = std_estimate, x = response, fill = type)) +
  viridis::scale_fill_viridis(begin = 0.5, end = 1, discrete = TRUE) +
  facet_grid(rows = vars(term)) +
  geom_col(position = position_dodge(width = .9)) +
  geom_linerange(aes(ymin = std_estimate - stdse, ymax = std_estimate + stdse),
    position = position_dodge(width = .9)) +
  labs(
    x = "Response variables",
    y = expression(paste("Standardized slope coefficients ", r[delta])),
    fill = "Model") +
  theme(legend.position = c(0.6, .05),
    legend.direction = "horizontal",
    text = element_text(size = 8), axis.text = element_text(size = 8)) +
  scale_y_continuous(sec.axis = sec_axis(~ ., name = "Predictive variable",
      breaks = NULL, labels = NULL))
```

```{r std, fig.cap=std_cap, fig.width=6, fig.height = 9}
semeff_tot %>%
  mutate(
    response = var_replacement()[response],
    predictor = var_replacement()[predictor]
    ) %>%
  ggplot(aes(x = predictor, y = effect, fill = effect_type)) +
  geom_col(
    position = position_dodge(width = 0.4), width = .4) +
  geom_hline(yintercept = 0) +
  geom_linerange(
    aes(ymin = lower_ci, ymax = upper_ci),
    position = position_dodge(width = 0.4)
    ) +
  facet_grid(rows = vars(response), cols = vars(model)) +
  labs(
    x = "Predictor",
    y = expression(paste("Standardized slope coefficients ", r[delta])),
    fill = "Effect type") +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

>>>>

```{r}
sp_semeff_tab <- from_semEff_to_table(sp_semeff)
semeff_tab <- from_semEff_to_table(semeff)
semeff_tot <- rbind(
  tibble(semeff_tab, model = "temporal"),
  tibble(sp_semeff_tab, model = "spatial")
  ) %>%
filter(
  !predictor %in% c("log_RC1", "log_RC2"),
  effect_type != "mediators"
)
```

@@

```{r std, fig.cap=std_cap, fig.width=7, fig.asp = .7}
p_sem_eff <- semeff_tot %>%
  mutate(
    response = var_replacement()[response],
    predictor = var_replacement()[predictor],
    effect_type = str_to_sentence(effect_type),
    model = str_to_sentence(model)
    ) %>%
  ggplot(aes(y = predictor, x = effect, colour = effect_type, shape = model)) +
  geom_point(
    position = position_dodge(width = 0.4), width = .4) +
  geom_vline(xintercept = 0) +
  geom_linerange(
    aes(xmin = lower_ci, xmax = upper_ci),
    position = position_dodge(width = 0.4)
    ) +
  facet_grid(rows = vars(response)) +
  labs(
    y = "Predictor",
    x = expression(paste("Standardized slope coefficients ", r[delta])),
    color = "Effect type", shape = "Model") +
  theme(legend.position = "bottom")
p_sem_eff
```
